### 2023-03-16 paper/icse24/tables/adv-comp-numbers.tex
icse24

\DefMacro{adv-comp-sa-model-under-test}{textattack/bert-base-uncased-SST-2}
\DefMacro{adv-comp-sa-alzantot-num-adv}{20}
\DefMacro{adv-comp-sa-alzantot-num-samples}{20}
\DefMacro{adv-comp-sa-alzantot-selfbleu-med}{0.373}
\DefMacro{adv-comp-sa-alzantot-selfbleu-avg}{0.373}
\DefMacro{adv-comp-sa-alzantot-selfbleu-std}{0.0}
\DefMacro{adv-comp-sa-alzantot-pdrcov-med}{170}
\DefMacro{adv-comp-sa-alzantot-pdrcov-avg}{170.0}
\DefMacro{adv-comp-sa-alzantot-pdrcov-std}{0.0}
\DefMacro{adv-comp-sa-bert-attack-num-adv}{25}
\DefMacro{adv-comp-sa-bert-attack-num-samples}{25}
\DefMacro{adv-comp-sa-bert-attack-selfbleu-med}{0.438}
\DefMacro{adv-comp-sa-bert-attack-selfbleu-avg}{0.438}
\DefMacro{adv-comp-sa-bert-attack-selfbleu-std}{0.0}
\DefMacro{adv-comp-sa-bert-attack-pdrcov-med}{178}
\DefMacro{adv-comp-sa-bert-attack-pdrcov-avg}{178.0}
\DefMacro{adv-comp-sa-bert-attack-pdrcov-std}{0.0}
\DefMacro{adv-comp-sa-pso-num-adv}{25}
\DefMacro{adv-comp-sa-pso-num-samples}{25}
\DefMacro{adv-comp-sa-pso-selfbleu-med}{0.411}
\DefMacro{adv-comp-sa-pso-selfbleu-avg}{0.411}
\DefMacro{adv-comp-sa-pso-selfbleu-std}{0.0}
\DefMacro{adv-comp-sa-pso-pdrcov-med}{178}
\DefMacro{adv-comp-sa-pso-pdrcov-avg}{178.0}
\DefMacro{adv-comp-sa-pso-pdrcov-std}{0.0}
\DefMacro{adv-comp-sa-ours-num-adv}{323}
\DefMacro{adv-comp-sa-ours-num-samples}{50}
\DefMacro{adv-comp-sa-ours-selfbleu-med}{0.437}
\DefMacro{adv-comp-sa-ours-selfbleu-avg}{0.435}
\DefMacro{adv-comp-sa-ours-selfbleu-std}{0.005}
\DefMacro{adv-comp-sa-ours-pdrcov-med}{264}
\DefMacro{adv-comp-sa-ours-pdrcov-avg}{262.0}
\DefMacro{adv-comp-sa-ours-pdrcov-std}{2.739}

>>>>

\DefMacro{adv-comp-sa-model-under-test}{textattack/bert-base-uncased-SST-2}
\DefMacro{adv-comp-sa-alzantot-num-adv}{20}
\DefMacro{adv-comp-sa-alzantot-num-samples}{20}
\DefMacro{adv-comp-sa-alzantot-selfbleu-med}{\textbf{0.373}}
\DefMacro{adv-comp-sa-alzantot-selfbleu-avg}{\textbf{0.373}}
\DefMacro{adv-comp-sa-alzantot-selfbleu-std}{\textbf{0.0}}
\DefMacro{adv-comp-sa-alzantot-pdrcov-med}{170}
\DefMacro{adv-comp-sa-alzantot-pdrcov-avg}{170.0}
\DefMacro{adv-comp-sa-alzantot-pdrcov-std}{0.0}
\DefMacro{adv-comp-sa-bert-attack-num-adv}{25}
\DefMacro{adv-comp-sa-bert-attack-num-samples}{25}
\DefMacro{adv-comp-sa-bert-attack-selfbleu-med}{0.438}
\DefMacro{adv-comp-sa-bert-attack-selfbleu-avg}{0.438}
\DefMacro{adv-comp-sa-bert-attack-selfbleu-std}{0.0}
\DefMacro{adv-comp-sa-bert-attack-pdrcov-med}{178}
\DefMacro{adv-comp-sa-bert-attack-pdrcov-avg}{178.0}
\DefMacro{adv-comp-sa-bert-attack-pdrcov-std}{0.0}
\DefMacro{adv-comp-sa-pso-num-adv}{25}
\DefMacro{adv-comp-sa-pso-num-samples}{25}
\DefMacro{adv-comp-sa-pso-selfbleu-med}{0.411}
\DefMacro{adv-comp-sa-pso-selfbleu-avg}{0.411}
\DefMacro{adv-comp-sa-pso-selfbleu-std}{0.0}
\DefMacro{adv-comp-sa-pso-pdrcov-med}{178}
\DefMacro{adv-comp-sa-pso-pdrcov-avg}{178.0}
\DefMacro{adv-comp-sa-pso-pdrcov-std}{0.0}
\DefMacro{adv-comp-sa-ours-num-adv}{\textbf{323}}
\DefMacro{adv-comp-sa-ours-num-samples}{50}
\DefMacro{adv-comp-sa-ours-selfbleu-med}{0.437}
\DefMacro{adv-comp-sa-ours-selfbleu-avg}{0.435}
\DefMacro{adv-comp-sa-ours-selfbleu-std}{0.005}
\DefMacro{adv-comp-sa-ours-pdrcov-med}{\textbf{264}}
\DefMacro{adv-comp-sa-ours-pdrcov-avg}{\textbf{262.0}}
\DefMacro{adv-comp-sa-ours-pdrcov-std}{\textbf{2.739}}

### 2023-03-16 paper/icse24/tables/lc-hsd-requirement-numbers.tex
icse24

\DefMacro{hsd_lc_1_search}{\textbf{Search}~hatecheck}

@@

\DefMacro{hsd_lc_2_search}{\textbf{Search}~hatecheck}

@@

\DefMacro{hsd_lc_3_search}{\textbf{Search}~hatecheck}

@@

\DefMacro{hsd_lc_4_search}{\textbf{Search}~hatecheck}

@@

\DefMacro{hsd_lc_5_search}{\textbf{Search}~hatecheck}

@@

\DefMacro{hsd_lc_6_search}{\textbf{Search}~hatecheck}

@@

\DefMacro{hsd_lc_7_search}{\textbf{Search}~seed=\{include: slur; label: toxic\}}

@@

\DefMacro{hsd_lc_8_search}{\textbf{Search}~seed=\{include: slur; label: non-toxic\}}

@@

\DefMacro{hsd_lc_9_search}{\textbf{Search}~seed=\{include: profanity; label: toxic\}}

@@

\DefMacro{hsd_lc_10_search}{\textbf{Search}~seed=\{include: profanity; label: non-toxic\}}

@@

\DefMacro{hsd_lc_11_search}{\textbf{Search}~toxic\_sent=\{include: identity; label: toxic\}, non\_toxic\_sent=\{include: identity; label: non-toxic\}}

@@

\DefMacro{hsd_lc_12_search}{\textbf{Search}~toxic\_sent=\{include: identity; label: toxic\}, non\_toxic\_sent=\{include: identity; label: non-toxic\}}

@@

\DefMacro{hsd_lc_17_search}{\textbf{Search}~seed=\{include: identity; exclude: pos adjs \& neg adjs \& pos nouns \& neg nouns \& pos verbs \& neg verbs; label: non-toxic\}}

@@

\DefMacro{hsd_lc_18_search}{\textbf{Search}~seed=\{include: identity; exclude: neg adjs \& neg nouns \& neg verbs; label: non-toxic\}}

>>>>

\DefMacro{hsd_lc_1_search}{\textbf{Search}~\textit{hatecheck}}

@@

\DefMacro{hsd_lc_2_search}{\textbf{Search}~\textit{hatecheck}}

@@

\DefMacro{hsd_lc_3_search}{\textbf{Search}~\textit{hatecheck}}

@@

\DefMacro{hsd_lc_4_search}{\textbf{Search}~\textit{hatecheck}}

@@

\DefMacro{hsd_lc_5_search}{\textbf{Search}~\textit{hatecheck}}

@@

\DefMacro{hsd_lc_6_search}{\textbf{Search}~\textit{hatecheck}}

@@

\DefMacro{hsd_lc_7_search}{\textbf{Search}~seed=\{include: \textit{slur}; label: toxic\}}

@@

\DefMacro{hsd_lc_8_search}{\textbf{Search}~seed=\{include: \textit{slur}; label: non-toxic\}}

@@

\DefMacro{hsd_lc_9_search}{\textbf{Search}~seed=\{include: \textit{profanity}; label: toxic\}}

@@

\DefMacro{hsd_lc_10_search}{\textbf{Search}~seed=\{include: \textit{profanity}; label: non-toxic\}}

@@

\DefMacro{hsd_lc_11_search}{\textbf{Search}~toxic\_sent=\{include: \textit{identity}; label: toxic\}, non\_toxic\_sent=\{include: \textit{identity}; label: non-toxic\}}

@@

\DefMacro{hsd_lc_12_search}{\textbf{Search}~toxic\_sent=\{include: \textit{identity}; label: toxic\}, non\_toxic\_sent=\{include: \textit{identity}; label: non-toxic\}}

@@

\DefMacro{hsd_lc_17_search}{\textbf{Search}~seed=\{include: \textit{identity}; exclude: pos adjs \& neg adjs \& pos nouns \& neg nouns \& pos verbs \& neg verbs; label: non-toxic\}}

@@

\DefMacro{hsd_lc_18_search}{\textbf{Search}~seed=\{include: \textit{identity}; exclude: neg adjs \& neg nouns \& neg verbs; label: non-toxic\}}

### 2023-03-16 paper/icse24/tables/test-results-all-numbers.tex
icse24

\DefMacro{test-results-all-lc7-num-exps}{492,817}

@@

\DefMacro{test-results-all-model0-lc7-num-fail}{158,854}
\DefMacro{test-results-all-model0-lc7-num-failrate}{28.31}
\DefMacro{test-results-all-model0-lc7-num-pass-to-fail}{9,748}

@@

\DefMacro{test-results-all-lc6-num-exps}{190,723}

@@

\DefMacro{test-results-all-model0-lc6-num-fail}{195,525}
\DefMacro{test-results-all-model0-lc6-num-failrate}{90.92}
\DefMacro{test-results-all-model0-lc6-num-pass-to-fail}{2,014}

@@

\DefMacro{test-results-all-lc5-num-exps}{102,304}

@@

\DefMacro{test-results-all-model0-lc5-num-fail}{120,451}
\DefMacro{test-results-all-model0-lc5-num-failrate}{99.65}
\DefMacro{test-results-all-model0-lc5-num-pass-to-fail}{71}

@@

\DefMacro{test-results-all-lc9-num-exps}{108,412}

@@

\DefMacro{test-results-all-model0-lc9-num-fail}{93,329}
\DefMacro{test-results-all-model0-lc9-num-failrate}{75.33}
\DefMacro{test-results-all-model0-lc9-num-pass-to-fail}{1,891}

@@

\DefMacro{test-results-all-lc2-num-exps}{507,091}

@@

\DefMacro{test-results-all-model0-lc2-num-fail}{134,641}
\DefMacro{test-results-all-model0-lc2-num-failrate}{23.12}
\DefMacro{test-results-all-model0-lc2-num-pass-to-fail}{18,510}

@@

\DefMacro{test-results-all-lc8-num-exps}{106,907}

@@

\DefMacro{test-results-all-model0-lc8-num-fail}{7,361}
\DefMacro{test-results-all-model0-lc8-num-failrate}{6.02}
\DefMacro{test-results-all-model0-lc8-num-pass-to-fail}{1,646}

@@

\DefMacro{test-results-all-model1-lc7-num-fail}{112,390}
\DefMacro{test-results-all-model1-lc7-num-failrate}{20.03}
\DefMacro{test-results-all-model1-lc7-num-pass-to-fail}{9,453}
\DefMacro{test-results-bl-model1-lc7-num-fail}{2,692}
\DefMacro{test-results-bl-model1-lc7-num-failrate}{31.57}

@@

\DefMacro{test-results-all-model1-lc6-num-fail}{157,635}
\DefMacro{test-results-all-model1-lc6-num-failrate}{73.30}
\DefMacro{test-results-all-model1-lc6-num-pass-to-fail}{7,289}

@@

\DefMacro{test-results-all-model1-lc5-num-fail}{120,054}

@@

\DefMacro{test-results-all-model1-lc5-num-pass-to-fail}{93}

@@

\DefMacro{test-results-all-model1-lc9-num-fail}{105,319}
\DefMacro{test-results-all-model1-lc9-num-failrate}{85.01}
\DefMacro{test-results-all-model1-lc9-num-pass-to-fail}{1,764}

@@

\DefMacro{test-results-all-model1-lc2-num-fail}{283,614}
\DefMacro{test-results-all-model1-lc2-num-failrate}{48.71}
\DefMacro{test-results-all-model1-lc2-num-pass-to-fail}{17,142}

@@

\DefMacro{test-results-all-model1-lc8-num-fail}{6,510}
\DefMacro{test-results-all-model1-lc8-num-failrate}{5.32}
\DefMacro{test-results-all-model1-lc8-num-pass-to-fail}{1,519}

@@

\DefMacro{test-results-all-model2-lc7-num-fail}{170,198}
\DefMacro{test-results-all-model2-lc7-num-failrate}{30.33}
\DefMacro{test-results-all-model2-lc7-num-pass-to-fail}{13,870}

@@

\DefMacro{test-results-all-model2-lc6-num-fail}{180,865}
\DefMacro{test-results-all-model2-lc6-num-failrate}{84.10}
\DefMacro{test-results-all-model2-lc6-num-pass-to-fail}{5,130}

@@

\DefMacro{test-results-all-model2-lc5-num-fail}{118,910}
\DefMacro{test-results-all-model2-lc5-num-failrate}{98.37}
\DefMacro{test-results-all-model2-lc5-num-pass-to-fail}{334}

@@

\DefMacro{test-results-all-model2-lc9-num-fail}{117,664}
\DefMacro{test-results-all-model2-lc9-num-failrate}{94.97}
\DefMacro{test-results-all-model2-lc9-num-pass-to-fail}{594}

@@

\DefMacro{test-results-all-model2-lc2-num-fail}{363,619}
\DefMacro{test-results-all-model2-lc2-num-failrate}{62.45}
\DefMacro{test-results-all-model2-lc2-num-pass-to-fail}{16,527}

@@

\DefMacro{test-results-all-model2-lc8-num-fail}{5,702}
\DefMacro{test-results-all-model2-lc8-num-failrate}{4.66}
\DefMacro{test-results-all-model2-lc8-num-pass-to-fail}{1,193}

>>>>

\DefMacro{test-results-all-lc7-num-exps}{465,291}

@@

\DefMacro{test-results-all-model0-lc7-num-fail}{152,009}
\DefMacro{test-results-all-model0-lc7-num-failrate}{28.49}
\DefMacro{test-results-all-model0-lc7-num-pass-to-fail}{8,878}

@@

\DefMacro{test-results-all-lc6-num-exps}{184,328}

@@

\DefMacro{test-results-all-model0-lc6-num-fail}{189,935}
\DefMacro{test-results-all-model0-lc6-num-failrate}{91.03}
\DefMacro{test-results-all-model0-lc6-num-pass-to-fail}{1,972}

@@

\DefMacro{test-results-all-lc5-num-exps}{97,897}

@@

\DefMacro{test-results-all-model0-lc5-num-fail}{116,049}
\DefMacro{test-results-all-model0-lc5-num-failrate}{99.64}
\DefMacro{test-results-all-model0-lc5-num-pass-to-fail}{67}

@@

\DefMacro{test-results-all-lc9-num-exps}{102,214}

@@

\DefMacro{test-results-all-model0-lc9-num-fail}{89,155}
\DefMacro{test-results-all-model0-lc9-num-failrate}{75.75}
\DefMacro{test-results-all-model0-lc9-num-pass-to-fail}{1,722}

@@

\DefMacro{test-results-all-lc2-num-exps}{343,214}

@@

\DefMacro{test-results-all-model0-lc2-num-fail}{99,312}
\DefMacro{test-results-all-model0-lc2-num-failrate}{23.74}
\DefMacro{test-results-all-model0-lc2-num-pass-to-fail}{10,357}

@@

\DefMacro{test-results-all-lc8-num-exps}{102,203}

@@

\DefMacro{test-results-all-model0-lc8-num-fail}{7,097}
\DefMacro{test-results-all-model0-lc8-num-failrate}{6.03}
\DefMacro{test-results-all-model0-lc8-num-pass-to-fail}{1,590}

@@

\DefMacro{test-results-all-model1-lc7-num-fail}{105,152}
\DefMacro{test-results-all-model1-lc7-num-failrate}{19.71}
\DefMacro{test-results-all-model1-lc7-num-pass-to-fail}{8,487}
\DefMacro{test-results-bl-model1-lc7-num-fail}{2,693}
\DefMacro{test-results-bl-model1-lc7-num-failrate}{31.58}

@@

\DefMacro{test-results-all-model1-lc6-num-fail}{153,686}
\DefMacro{test-results-all-model1-lc6-num-failrate}{73.66}
\DefMacro{test-results-all-model1-lc6-num-pass-to-fail}{7,007}

@@

\DefMacro{test-results-all-model1-lc5-num-fail}{115,676}

@@

\DefMacro{test-results-all-model1-lc5-num-pass-to-fail}{90}

@@

\DefMacro{test-results-all-model1-lc9-num-fail}{100,351}
\DefMacro{test-results-all-model1-lc9-num-failrate}{85.26}
\DefMacro{test-results-all-model1-lc9-num-pass-to-fail}{1,452}

@@

\DefMacro{test-results-all-model1-lc2-num-fail}{208,313}
\DefMacro{test-results-all-model1-lc2-num-failrate}{49.79}
\DefMacro{test-results-all-model1-lc2-num-pass-to-fail}{11,472}

@@

\DefMacro{test-results-all-model1-lc8-num-fail}{6,226}
\DefMacro{test-results-all-model1-lc8-num-failrate}{5.29}
\DefMacro{test-results-all-model1-lc8-num-pass-to-fail}{1,489}

@@

\DefMacro{test-results-all-model2-lc7-num-fail}{162,426}
\DefMacro{test-results-all-model2-lc7-num-failrate}{30.44}
\DefMacro{test-results-all-model2-lc7-num-pass-to-fail}{12,729}

@@

\DefMacro{test-results-all-model2-lc6-num-fail}{175,323}
\DefMacro{test-results-all-model2-lc6-num-failrate}{84.02}
\DefMacro{test-results-all-model2-lc6-num-pass-to-fail}{5,003}

@@

\DefMacro{test-results-all-model2-lc5-num-fail}{114,556}
\DefMacro{test-results-all-model2-lc5-num-failrate}{98.35}
\DefMacro{test-results-all-model2-lc5-num-pass-to-fail}{325}

@@

\DefMacro{test-results-all-model2-lc9-num-fail}{111,874}
\DefMacro{test-results-all-model2-lc9-num-failrate}{95.05}
\DefMacro{test-results-all-model2-lc9-num-pass-to-fail}{575}

@@

\DefMacro{test-results-all-model2-lc2-num-fail}{262,994}
\DefMacro{test-results-all-model2-lc2-num-failrate}{62.86}
\DefMacro{test-results-all-model2-lc2-num-pass-to-fail}{9,808}

@@

\DefMacro{test-results-all-model2-lc8-num-fail}{5,470}
\DefMacro{test-results-all-model2-lc8-num-failrate}{4.65}
\DefMacro{test-results-all-model2-lc8-num-pass-to-fail}{1,151}
